`r params$doc_title`

### 2023-02-08 scripts/MSc.Rmd
added loop for performance measure tables and figures

library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(tibble)
library(ggplot2)
library(ggdist)
library(gghalves)
library(ggthemes)
library(ggpubr)
library(scales)
#library(biomaRt)  # different script
library(kableExtra)
library(MendelianRandomization)
library(TwoSampleMR)
library(mr.raps)
library(MRMix)
library(MRPRESSO)
library(penalized)
library(conflicted)
source("helper/MR_lasso.R")  # Slob&Burgess 2020
source("helper/PVE_calculation_fns.R") 
source("helper/plotfigure01fn.R") 
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
```

@@

t(filter_FTO) %>% kable() %>% 
  kable_styling(font_size=10)
```

@@

# for the numeric traits we have to map over sample size and recalculate se_updated
n.orig_sqrt <- sqrt(n.orig)
explained_variance_BMI2_sample_size <- map(n, ~explained_variance_numeric2(maf = my_data_harm$eaf.bmi, beta = my_data_harm$beta.bmi, 
                                                                           se_beta = abs(my_data_harm$beta.bmi / -qnorm(p=(my_data_harm$p.value.bmi / 2), mean = 0) * n.orig_sqrt / sqrt(.x)), 
                                                                           samplesize = .x))

@@

ggplot(df_cum_expl_var, aes(x=n))+
  geom_line(aes(y=cum_expl_varX2_sample_size*100), col="red")+
  geom_line(aes(y=cum_expl_varX2*100))
```

@@

# Dual Y axis: we have 284 IVs, scale them to 5% (y-axis [0;5%]): 3/284 
## https://r-graph-gallery.com/line-chart-dual-Y-axis-ggplot2.html
scale_factor <- 4.5/284

@@

## load results from script `perform_mr.R`
est.bmi.gsd <- readRDS(file = dplyr::last(list.files("../output/Rdata/", pattern = "_est_BMI_GSD.rds", full.names = TRUE)))

@@

# read dat from "simstudy.R"  #------------------------------------------------
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
```

@@

# EXPOSURE PVE
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  pivot_longer(everything(), names_to = "PVE_X", values_to = "value_X") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_X_sim
# # CONFOUNDER PVE
# est_sim %>% 
#   select(!!!(colname_pve_U)) %>% 
#   pivot_longer(everything(), names_to = "PVE_U", values_to = "value_U") %>% 
#   cbind(sample_size_filtered) %>% as_tibble() -> pve_U_sim
# # OUTCOME PVE
# est_sim %>% 
#   select(!!!(colname_pve_Y)) %>% 
#   pivot_longer(everything(), names_to = "PVE_Y", values_to = "value_Y") %>% 
#   cbind(sample_size_filtered) %>% as_tibble() -> pve_Y_sim

@@

```{r further-metrics}
# coverage
coverage <- function(thetaobs, thetaobs_se, theta, ...) {
  lower_ci <- thetaobs - thetaobs_se
  upper_ci <- thetaobs + thetaobs_se
  coverage <- mean(lower_ci <= theta & upper_ci >= theta)
  return(coverage)
}
# coverage bias eliminated
coverage_bias_eliminated <- function(thetaobs, thetaobs_se, ...) {
  lower_ci <- thetaobs - thetaobs_se
  upper_ci <- thetaobs + thetaobs_se
  mean_thetaobs <- mean(thetaobs)
  coverage_bias_eliminated <- mean(lower_ci <= mean_thetaobs & upper_ci >=mean_thetaobs)
  return(coverage_bias_eliminated)
}
# type1error
type1error <- function(pvals) sum(pvals<=0.05)/length(pvals)  # no causal_effect

@@

  ## GBC additional metrics ----------------------------------------------------
  # deleted 2023-01-29
}
```

@@

@@

```{r theta-sim-distribution-GSD-old, eval=FALSE, fig.height=6, fig.width=10, include=FALSE}
### OLD
# # compare distribution of simulated thetas against theta_324000
# boxplot_dat <- est_sim %>% 
#   select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
#   pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
#   mutate(theta_sim_numeric = format(as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")), scientific=FALSE))
# 
# ggplot(boxplot_dat, aes(x=forcats::fct_rev( as.factor(theta_sim_numeric)), y=value)) +
#   geom_boxplot()+
#   geom_jitter(width=0.1,alpha=0.2)+
#   geom_hline(yintercept=  args.gsd.ivw$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
#   annotate(geom = "text", x = "300000", y = args$theta+0.5,
#            label= expression( paste("ref: ", theta[X] ))  , 
#            color= ggthemes_data$few$colors$Dark[9,2][[1]]
#              )+
#   scale_x_discrete(name = paste0("Size of sample ", as.roman(1)),  breaks = c(" 50000", "100000", "150000", "200000", "250000", "300000"), )+ 
#   ylab(expression(paste(theta[sim], " with ", n[sim]== 25 ) )  ) +
#   labs(title = "Estimates from beta simulation",
#        caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
#        )+
#   coord_flip()+
#   theme_few() -> simplot_thetas
# simplot_thetas
```

@@

ggarrange(bias_mse_plot_IVW_GSD, bias_mse_plot_MODE_GSD, bias_mse_plot_CONMIX_GSD, bias_mse_plot_MRMIX_GSD
          ncol = 1, nrow = 4, common.legend = TRUE) -> bias_mse_plot_GSD
bias_mse_plot_GSD

@@

@@

@@

```{r parallel-performance}

funs <- c(mean = mean, emp_se=emp_se, bias = bias, mse = mse)  # as above

for (true_method in 1:length(selected_true_methods)) {
  print(true_method)

  # define reference estimate for all 5 chosen methods in loop 
  args.gsd.method <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == selected_true_methods[true_method]], 
                          nsim=nrow(est_sim)
  )

@@

  ## combine metrics
  IVW_GSD_performance_metrics <- IVW_GSD_performance_metrics %>% 
    select(N, everything()) %>% 
    cbind(data.frame(IVW_GSD_coverage_calc, IVW_GSD_coverage_bias_eliminated_calc, IVW_GSD_type1error_calc)) %>% 
    as_tibble()
  MODE_GSD_performance_metrics <- MODE_GSD_performance_metrics %>% 
    select(N, everything()) %>% 
    cbind(data.frame(MODE_GSD_coverage_calc, 
                     MODE_GSD_coverage_bias_eliminated_calc, MODE_GSD_type1error_calc)) %>% 
    as_tibble()
  CONMIX_GSD_performance_metrics <- CONMIX_GSD_performance_metrics %>% 
    select(N, everything()) %>% 
    cbind(data.frame(CONMIX_GSD_coverage_calc, 
                     CONMIX_GSD_coverage_bias_eliminated_calc, CONMIX_GSD_type1error_calc)) %>% 
    as_tibble()
  MRMIX_GSD_performance_metrics <- MRMIX_GSD_performance_metrics %>% 
    select(N, everything()) %>% 
    cbind(data.frame(MRMIX_GSD_coverage_calc, 
                     MRMIX_GSD_coverage_bias_eliminated_calc, MRMIX_GSD_type1error_calc)) %>% 
    as_tibble()
  MRMIX_GSD_performance_metrics %>% 
    mutate(across(cols = where(is.numeric), round(3))) %>% 
    kable(caption = "MRMIX method on BMI -> GSD performance metrics") %>% 
    kable_styling(font_size=10)

>>>>

library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(tibble)
library(ggplot2)
library(ggdist)
library(gghalves)
library(ggthemes)
library(ggpubr)
library(scales)
#library(biomaRt)  # different script
library(kableExtra)
library(MendelianRandomization)
library(TwoSampleMR)
library(mr.raps)
library(MRMix)
library(MRPRESSO)
library(penalized)
# library(rsimsum)   do not use
library(conflicted)
source("helper/MR_lasso.R")  # Slob&Burgess 2020
source("helper/PVE_calculation_fns.R") 
source("helper/plotfigure01fn.R") 
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
# conflict_prefer("kable", "kableExtra")
```

@@

t(filter_FTO) %>%  kableExtra::kable() %>% 
  kable_styling(font_size=10)
```

@@

# for the numeric traits we have to map over sample size and recalculate se_updated
explained_variance_BMI2_sample_size <- map(n, ~explained_variance_numeric2(maf = my_data_harm$eaf.bmi, beta = my_data_harm$beta.bmi, 
                                                                           se_beta = abs(my_data_harm$beta.bmi / -qnorm(p=(my_data_harm$p.value.bmi / 2), mean = 0) * sqrt(n.orig) / sqrt(.x)), 
                                                                           samplesize = .x))

@@

ggplot(df_cum_expl_var, aes(x=n))+
  geom_line(aes(y=cum_expl_varX2_sample_size*100), col="red")+  # slightly higher PVE if samplesize mapped into PVE_X formula
  geom_line(aes(y=cum_expl_varX2*100))
```

@@

# Dual Y axis: we have 284 IVs, scale them to 5% (y-axis [0;5%]): 3/284 
## https://r-graph-gallery.com/line-chart-dual-Y-axis-ggplot2.html
scale_factor <- 4.5/284
N_annotation <- c(10000, 100000, 200000, 300000)

@@

## load results from script `perform_mr.R`
est.bmi.gsd <- readRDS(dplyr::last(list.files("../output/Rdata/", pattern = "_est_BMI_GSD.rds", full.names = TRUE)))

@@

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
```

@@

# EXPOSURE PVE
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  pivot_longer(everything(), names_to = "PVE_X", values_to = "value_X") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_X_sim

# mean PVE per sample size
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  map(~mean(.x)) %>% 
  unlist() -> PVE_X_sim_mean

@@

```{r}
# print("95% Confidence Interval: [{:.2f}, {:.2f}]".format(lower_bound, upper_bound))
```

```{r further-metrics}
# coverage
coverage <- function(thetaobs, thetaobs_se, theta, ...) {
  # https://www.r-bloggers.com/2021/11/calculate-confidence-intervals-in-r/
  lower_ci <- thetaobs - 1.96*thetaobs_se
  upper_ci <- thetaobs + 1.96*thetaobs_se
  coverage <- mean(lower_ci <= theta & upper_ci >= theta)
  return(coverage)
}

# coverage bias eliminated
coverage_bias_eliminated <- function(thetaobs, thetaobs_se, ...) {
  lower_ci <- thetaobs - 1.96*thetaobs_se
  upper_ci <- thetaobs + 1.96*thetaobs_se
  mean_thetaobs <- mean(thetaobs)
  coverage_bias_eliminated <- mean(lower_ci <= mean_thetaobs & upper_ci >=mean_thetaobs)
  return(coverage_bias_eliminated)
}
# type1error
type1error <- function(pvals) sum(pvals<=0.05)/length(pvals)  # no causal_effect

@@

@@

```{r}
#s1 <- simsum(data = est_sim, estvarname = "IVW_theta_sim_BMI_GSD_40000", se = "IVW_theta_se_sim_BMI_GSD_40000", true = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "IVW"] )

## stats param
# • nsim,the number of replications with non-missing point estimates and standard error.
# • thetamean, average point estimate.
# • thetamedian, median point estimate.
# • se2mean, average variance.
# • se2median, median variance.
# • bias, bias in point estimate.
# • empse, empirical standard error.
# • mse, mean squared error.
# • relprec, percentage gain in precision relative to the reference method.
# • modelse, model-based standard error.
# • relerror, relative percentage error in standard error.
# • cover, coverage of a nominal level\
# • becover, bias corrected coverage of a nominal level\
# • power, power of a (1 - level)\

#statsparam <- c("nsim", "thetamean", "se2mean", "bias", "empse", "mse", "cover", "becover", "power")
#simsum_summary <- summary(s1, stats = statsparam)
```

---

@@

@@

ggarrange(bias_mse_plot_IVW_GSD, bias_mse_plot_MODE_GSD, bias_mse_plot_CONMIX_GSD, bias_mse_plot_MRMIX_GSD,
          ncol = 1, nrow = 4, common.legend = TRUE) -> bias_mse_plot_GSD
bias_mse_plot_GSD

@@

---

@@

## Calculate performance measures

@@

```{r parallel-performance}
for (true_method in 1:length(selected_true_methods)) {
  # define reference estimate for ALL 5 chosen methods in loop 
  args.gsd.method <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == selected_true_methods[true_method]], 
                          nsim=nrow(est_sim)
  )

@@

  ## combine metrics
  IVW_GSD_performance_metrics <- IVW_GSD_performance_metrics %>% 
    select(N, everything()) %>% 
    cbind(data.frame(IVW_GSD_coverage_calc, IVW_GSD_coverage_bias_eliminated_calc, IVW_GSD_type1error_calc)) %>% 
    as_tibble()
  MODE_GSD_performance_metrics <- MODE_GSD_performance_metrics %>% 
    select(N, everything()) %>% 
    cbind(data.frame(MODE_GSD_coverage_calc, 
                     MODE_GSD_coverage_bias_eliminated_calc, MODE_GSD_type1error_calc)) %>% 
    as_tibble()
  CONMIX_GSD_performance_metrics <- CONMIX_GSD_performance_metrics %>% 
    select(N, everything()) %>% 
    cbind(data.frame(CONMIX_GSD_coverage_calc, 
                     CONMIX_GSD_coverage_bias_eliminated_calc, CONMIX_GSD_type1error_calc)) %>% 
    as_tibble()
  MRMIX_GSD_performance_metrics <- MRMIX_GSD_performance_metrics %>% 
    select(N, everything()) %>% 
    cbind(data.frame(MRMIX_GSD_coverage_calc, 
                     MRMIX_GSD_coverage_bias_eliminated_calc, MRMIX_GSD_type1error_calc)) %>% 
    as_tibble()

  # STORE
  filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_IVW_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = IVW_GSD_performance_metrics, file = filename.IVW_table.performance)
  filename.MODE_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_MODE_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = MODE_GSD_performance_metrics, file = filename.MODE_table.performance)
  filename.CONMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_CONMIX_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = CONMIX_GSD_performance_metrics, file = filename.CONMIX_table.performance)
  filename.MRMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_MRMIX_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = MRMIX_GSD_performance_metrics, file = filename.MRMIX_table.performance)

  ###
  ## PLOT  -------------------------------------------------------------------
  IVW_BMI_GSD_geom_point_dat <- est_sim %>% 
    select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
    pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
    mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

  ggplot(IVW_GSD_performance_metrics, aes(x=N, y=IVW_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    # geom_errorbar(aes(ymin=IVW_GSD_mean-1.96*IVW_GSD_emp_se, ymax=IVW_GSD_mean+1.96*IVW_GSD_emp_se), 
    #               width=3000, # x-axis dimension
    #               position = "dodge")+
    ## ADD rainbow plots
    geom_boxplot(data = IVW_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = IVW_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = IVW_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("IVW estimate: BMI -> GSD\nSelected Reference Method: ", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> IVW_GSD_simplot_thetas

  ggplot(MODE_GSD_performance_metrics, aes(x=N, y=MODE_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    # geom_errorbar(aes(ymin=MODE_GSD_mean-1.96*MODE_GSD_emp_se, ymax=MODE_GSD_mean+1.96*MODE_GSD_emp_se), 
    #               width=3000, # x-axis dimension
    #               position = "dodge")+
    ## ADD rainbow plots
    geom_boxplot(data = MODE_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = MODE_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = MODE_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("MODE estimate: BMI -> GSD\nSelected Reference Method: ", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> MODE_GSD_simplot_thetas

  ggplot(CONMIX_GSD_performance_metrics, aes(x=N, y=CONMIX_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    ## ADD rainbow plots
    geom_boxplot(data = CONMIX_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = CONMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = CONMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("CONMIX estimate: BMI -> GSD\nSelected Reference Method: ", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> CONMIX_GSD_simplot_thetas

  ggplot(MRMIX_GSD_performance_metrics, aes(x=N, y=MRMIX_GSD_mean))+ 
    geom_point()+
    geom_hline(yintercept=  args.gsd.method$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    annotate(geom = "text", x = 50000, y = args.gsd.method$theta+0.05,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
    ## ADD rainbow plots
    geom_boxplot(data = MRMIX_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                 col=ggthemes_data$few$colors$Dark[3,2][[1]],
                 alpha=0.2, size=0.2, outlier.shape = NA)+
    ggdist::stat_halfeye(data = MRMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                         inherit.aes = FALSE, 
                         slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                         geom = "slabinterval",
                         na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
    gghalves::geom_half_point(
      data = MRMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
      inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
      side = "l", range_scale = .4, alpha = .2)+
    ## FINISH rainbow
    scale_x_continuous(labels = comma)+
    xlab("Size of Sample I")+
    ylab("Mean thetas")+
    scale_y_continuous(limits = c(0.25,0.8))+
    labs(title = "Simulated Thetas with Empirical Standard Error", 
         subtitle = paste0("MRMIX estimate: BMI -> GSD\nSelected Reference Method: ", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> MRMIX_GSD_simplot_thetas

  # SAVE
  filename_IVW_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_IVW_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  ggsave(filename = filename_IVW_GSD_simplot_thetas, plot = IVW_GSD_simplot_thetas, 
         width = 15, height = 6, 
         units = "in"  # default
         )
  filename_MODE_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MODE_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  ggsave(filename = filename_MODE_GSD_simplot_thetas, plot = MODE_GSD_simplot_thetas, 
         width = 15, height = 6, 
         units = "in"  # default
         )
  filename_CONMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  ggsave(filename = filename_CONMIX_GSD_simplot_thetas, plot = CONMIX_GSD_simplot_thetas, 
         width = 15, height = 6, 
         units = "in"  # default
         )
  filename_MRMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MRMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  ggsave(filename = filename_MRMIX_GSD_simplot_thetas, plot = MRMIX_GSD_simplot_thetas, 
         width = 15, height = 6, 
         units = "in"  # default
         )

  IVW_GSD_simplot_thetas$labels$title <- ""
  MODE_GSD_simplot_thetas$labels$title <- ""
  CONMIX_GSD_simplot_thetas$labels$title <- ""
  MRMIX_GSD_simplot_thetas$labels$title <- ""
  ggarrange(IVW_GSD_simplot_thetas,MODE_GSD_simplot_thetas,CONMIX_GSD_simplot_thetas, MRMIX_GSD_simplot_thetas,
            ncol = 1, nrow = 4) -> GSD_simplot_thetas_arrange
  GSD_simplot_thetas_arrange

  filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
         width = 10, height = 22, 
         units = "in"  # default
         )

  ### GSD Bias & MSE
  #BIAS
  ggplot(IVW_GSD_performance_metrics, aes(x=N, y=IVW_GSD_bias))+ 
    geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    scale_x_continuous(labels = comma)+
    scale_y_continuous(limits = c(-1.5,1.5))+
    xlab("Size of Sample I")+
    ylab("Bias")+
    labs(title = "IVW estimate: BMI -> GSD",
         caption = paste0("Selected Reference Method:\n", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> biasplot_IVW_GSD
  #MSE
  ggplot(IVW_GSD_performance_metrics, aes(x=N, y=IVW_GSD_mse))+ 
    geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    scale_x_continuous(labels = comma)+
    scale_y_continuous(limits = c(0,1.8))+
    xlab("Size of Sample I")+
    ylab("MSE")+
    labs(title = "IVW estimate: BMI -> GSD",
         caption = paste0("Selected Reference Method:\n", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> mseplot_IVW_GSD
  ggarrange(biasplot_IVW_GSD, mseplot_IVW_GSD) -> bias_mse_plot_IVW_GSD

  ## MODE
  ggplot(MODE_GSD_performance_metrics, aes(x=N, y=MODE_GSD_bias))+ 
    geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    scale_x_continuous(labels = comma)+
    scale_y_continuous(limits = c(-1.5,1.5))+
    xlab("Size of Sample I")+
    ylab("Bias")+
    labs(title = "MODE estimate: BMI -> GSD",
         caption = paste0("Selected Reference Method:\n", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> biasplot_MODE_GSD
  ggplot(MODE_GSD_performance_metrics, aes(x=N, y=MODE_GSD_mse))+ 
    geom_point()+
      geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    scale_x_continuous(labels = comma)+
    scale_y_continuous(limits = c(0,1.8))+
    xlab("Size of Sample I")+
    ylab("MSE")+
    labs(title = "MODE estimate: BMI -> GSD",
         caption = paste0("Selected Reference Method:\n", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> mseplot_MODE_GSD
  ggarrange(biasplot_MODE_GSD, mseplot_MODE_GSD) -> bias_mse_plot_MODE_GSD

  ## CONMIX
  ggplot(CONMIX_GSD_performance_metrics, aes(x=N, y=CONMIX_GSD_bias))+ 
    geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    scale_x_continuous(labels = comma)+
    scale_y_continuous(limits = c(-1.5,1.5))+
    xlab("Size of Sample I")+
    ylab("Bias")+
    labs(title = "CONMIX estimate: BMI -> GSD",
         caption = paste0("Selected Reference Method:\n", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> biasplot_CONMIX_GSD
  ggplot(CONMIX_GSD_performance_metrics, aes(x=N, y=CONMIX_GSD_mse))+ 
    geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    scale_x_continuous(labels = comma)+
    scale_y_continuous(limits = c(0,1.8))+
    xlab("Size of Sample I")+
    ylab("MSE")+
    labs(title = "CONMIX estimate: BMI -> GSD",
         caption = paste0("Selected Reference Method:\n", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> mseplot_CONMIX_GSD
  ggarrange(biasplot_CONMIX_GSD, mseplot_CONMIX_GSD) -> bias_mse_plot_CONMIX_GSD

  ## MRMIX
  ggplot(MRMIX_GSD_performance_metrics, aes(x=N, y=MRMIX_GSD_bias))+ 
    geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    scale_x_continuous(labels = comma)+
    scale_y_continuous(limits = c(-1.5,1.5))+
    xlab("Size of Sample I")+
    ylab("Bias")+
    labs(title = "MRMIX estimate: BMI -> GSD",
         caption = paste0("Selected Reference Method:\n", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> biasplot_MRMIX_GSD
  ggplot(MRMIX_GSD_performance_metrics, aes(x=N, y=MRMIX_GSD_mse))+ 
    geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
    scale_x_continuous(labels = comma)+
    scale_y_continuous(limits = c(0,1.8))+
    xlab("Size of Sample I")+
    ylab("MSE")+
    labs(title = "MRMIX estimate: BMI -> GSD",
         caption = paste0("Selected Reference Method:\n", 
                           selected_true_methods[true_method], 
                           " estimate calculated with total sample size"))+
    theme_few() -> mseplot_MRMIX_GSD
  ggarrange(biasplot_MRMIX_GSD, mseplot_MRMIX_GSD) -> bias_mse_plot_MRMIX_GSD

  ggarrange(bias_mse_plot_IVW_GSD, bias_mse_plot_MODE_GSD, bias_mse_plot_CONMIX_GSD, bias_mse_plot_MRMIX_GSD,
            ncol = 1, nrow = 4, common.legend = TRUE) -> bias_mse_plot_GSD
  bias_mse_plot_GSD

  filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_REF_METHOD_", selected_true_methods[true_method], "_NSIM_",nsim, ".png")
  ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
         width = 7, height = 12, 
         units = "in"  # default
         )
}
```
